---
title: A N A L Y T I C S <br>[FE Uprating Factors]
author: Bogdan Micu
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    toc_depth: 3
mainfont: Calibri
---

<!-- ------------- START LAYOUT SETUP ------------- -->

<!-- LOGO -->

<script>
  $(document).ready(function() {
    $('#TOC').parent().prepend('<div id=\"nav_logo\"><img src=\"https://ec.europa.eu/eurostat/cache/digpub/european_economy/vis/chapter21_1/images/logoestat.png\"></div>');
  });
</script>

<!-- STYLE -->

<style>
#nav_logo {
  width: 100%;
  margin-top: 20px;
}
#TOC {
  background: url("https://ec.europa.eu/eurostat/documents/10186/8486739/experimental-blue.png");
  background-size: contain;
  padding-top: 77px !important;
  background-repeat: no-repeat;
}

h1.title {
  font-size: 27px;
  font-weight: bold;
  color: DarkRed;
  text-align:center;
}

body {
  font-size: 17px;
  font-family: Calibri;
  color: #273749;
  text-align:justify;
}

a, a:hover {
    color: cornflowerblue;
}

.nav>li>a {
  position: relative;
  padding: 3px 9px;
}

div.tocify {
  max-width: 17%;
}

</style>

```{r SETUP, message=FALSE, warning=FALSE, include=FALSE}

knitr::opts_chunk$set(dpi=99,
                      out.width="100%",
                      message=FALSE,
                      warning=FALSE,
                      echo=FALSE) # dev=c("png","svg"), fig.ext="png"

```
<!-- ------------- END LAYOUT SETUP ------------- -->


```{r echo=FALSE}

download.file(url="https://ec.europa.eu/eurostat/documents/7894008/9036137/IncomeEquality120.png",
              destfile=here("OUTILS","MIX","logo.png"),
              mode="wb")

htmltools::img(src=knitr::image_uri(here("OUTILS","MIX","logo.png")), 
               alt='logo', 
               style='position:absolute; top:0; right:0; padding:9px; height:111px; width:111px')

```

```{r Data & Funs, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

source(here("OUTILS","FUNS","Fviz_model.R"))
load(here("DATA","item_list.Rdata"))
load(here("DATA","predictor_list.Rdata"))
load(here("DATA","uf_em.Rdata"))

```


```{r , echo=FALSE, message=FALSE}

f.block.indicator=function (.v) {
  paste0("\n### ",
         {if (str_detect(.v,"Generic")) "<i>[Generic<br>Predictors]</i>"
           else paste0(gsub(" @ ","<br><span style=\'font-size:9pt\'>",.v),
                             "</span>")},
         " {.tabset .tabset-pills}\n",
         "\n#### FORECASTS {.tabset .tabset-dropdown}\n",
         "\n##### All Models\n",
         "```{r}\n
         F.viz.model(.viz=\"index\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE)\n
         F.viz.model(.viz=\"yoy\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE)\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         {if (str_detect(.v,"Generic")) ""
           else 
           paste0("\n##### Univariate Linear\n",
         "```{r}\n
         F.viz.model(.viz=\"index\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.lm1\")\n
         F.viz.model(.viz=\"yoy\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.lm1\")\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         "\n##### Univariate Linear w/ ARIMA errors\n",
         "```{r}\n
         F.viz.model(.viz=\"index\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.ar1\")\n
         F.viz.model(.viz=\"yoy\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.ar1\")\n
         ```\n",
         "\n<p>\n***\n<p>\n")},
         {if (str_detect(.v,"Generic") |
              !.v %in% gsub("`","",generic.predictors))
           paste0("\n##### Multivariate Linear\n",
         "```{r}\n
         F.viz.model(.viz=\"index\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.lmx\")\n
         F.viz.model(.viz=\"yoy\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.lmx\")\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         "\n##### Multivariate Linear w/ ARIMA errors\n",
         "```{r}\n
         F.viz.model(.viz=\"index\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.arx\")\n
         F.viz.model(.viz=\"yoy\",.fxt=TRUE,.silc=\"",.s,"\",.var=\"",.v,"\",show.var=FALSE,.model=\"m.arx\")\n
         ```\n",
         "\n<p>\n***\n<p>\n")
           else ""},
         {if (str_detect(.v,"Generic")) ""
           else 
           paste0("\n#### SILC vs<br>Uprating Factor {.tabset .tabset-pills}\n",
         "\n##### 2008-2018\n",
         "```{r}\n
         F.viz.model(.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"index\")\n
         F.viz.model(.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         "\n##### 2008-2012\n",
         "```{r}\n
         F.viz.model(.data=filter(data.x,YEAR %in% 2008:2012),.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"index\")\n
         F.viz.model(.data=filter(data.x,YEAR %in% 2008:2012),.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=filter(data.x,YEAR %in% 2008:2012),.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n")},
         "\n#### Modeling Performance :<br>Model Fit {.tabset .tabset-dropdown}\n",
         {if (str_detect(.v,"Generic")) ""
           else 
           paste0("\n##### Univariate Linear\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.lm1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.lm1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         "\n##### Univariate Linear w/ ARIMA errors\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.ar1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.ar1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n")},
         {if (str_detect(.v,"Generic") |
              !.v %in% gsub("`","",generic.predictors))
           paste0("\n##### Multivariate Linear\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.lmx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.lmx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         "\n##### Multivariate Linear w/ ARIMA errors\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.arx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"EST\",.model=\"m.arx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n")
           else ""},
         "\n#### Modeling Performance :<br>Forecast {.tabset .tabset-dropdown}\n",
         {if (str_detect(.v,"Generic")) ""
           else 
           paste0("\n##### Univariate Linear\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.lm1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.lm1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         "\n##### Univariate Linear w/ ARIMA errors\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.ar1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.ar1\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n")},
         {if (str_detect(.v,"Generic") |
              !.v %in% gsub("`","",generic.predictors))
           paste0("\n##### Multivariate Linear\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.lmx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.lmx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n",
         "\n##### Multivariate Linear w/ ARIMA errors\n",
         "```{r}\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.arx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"yoy\")\n
         F.viz.model(.data=data.model,.source=\"FXT.2\",.model=\"m.arx\",.silc=\"",.s,"\",.var=\"",.v,"\",.viz=\"cor\")\n
         ```\n",
         "\n<p>\n***\n<p>\n")
           else ""})
}

out=NULL
for (.s in unique(names(predictor.list))) {
  out=c(out,
        paste0("\n# `r '",.s,"'` {.tabset .tabset-pills}\n",
               "\n## EUROMOD\n",
               {if (.s %in% unique(UF.EM$SILC.INDICATOR))
                 paste0("```{r, fig.width=11, fig.height=9}\n",
               "F.viz.EUROMOD(.s_=\"",.s,"\",.v_=\"index\")\n
               F.viz.EUROMOD(.s_=\"",.s,"\",.v_=\"yoy\")\n
               F.viz.EUROMOD(.s_=\"",.s,"\",.v_=\"cor\")\n```\n")
               else "NO EUROMOD Uprating Factor\n\n"},
               "\n<p>\n***\n<p>\n",
               "\n## Alternative Uprating Factors {.tabset .tabset-pills}\n",
               "\n### FORECASTS\n",
               "```{r}\n
               F.viz.model(.viz=\"index\",.fxt=TRUE,.silc=\"",.s,"\",show.var=FALSE)\n
               F.viz.model(.viz=\"yoy\",.fxt=TRUE,.silc=\"",.s,"\",show.var=FALSE)\n
               ```\n",
               "\n<p>\n***\n<p>\n"),
        knitr::knit_expand(text=paste(lapply(
          c("[Generic Predictors]",
            predictor.list[which(names(predictor.list)==.s)]),
          f.block.indicator),collapse="\n\n")))
}

```
`r paste(knitr::knit(text=out), collapse='\n')`



